### 2023-08-29 README.Rmd
fin 230829

<li><code>freqassort</code>: Inspired by the former <a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment.
Again, you have to define a `none` alternative, because `freqassort` uses the *threshold* approach,
meaning if the utility of one product is above the utility of `none`,
it is marked as potential purchase option.</li>

<li><code>reach</code>: Inspired by the former
<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. `reach` also uses the *threshold* approach (see above).</li>

@@

```{r}
accuracy(
  data = HOT, # data frame
  opts = c(Option_1:None), # column names of alternatives
  choice = choice, # column name of choice
  none = None # column name of none alternative
)
```
Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers. We will use the <code>reach()</code> function and use the threshold approach. To specify the bundles we are offering we use the <code>opts</code> argument in our function.

@@

@@

>>>>

<li><code>turf</code>: **T**(otal) **U**(nduplicated) **R**(each) and **F**(requency) is a "product line extension model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option). <code>turf</code> currently provides both the threshold approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p. 112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p. 111).

<li><code>freqassort</code>: Similar to <code>turf</code>, <code>freqassort</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment. 
Again, you have to define a `none` alternative, because `freqassort` uses the *threshold* approach,
meaning if the utility of one product is above the utility of `none`,
it is marked as potential purchase option. While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>freqassort</code>.</li>

<li><code>reach</code>: Similar to <code>turf</code>,, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. `reach` also uses the *threshold* approach (see above). While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>reach</code></li>

@@

```{r}
accuracy(
  data = HOT, # data frame
  opts = c(Option_1:None), # column names of alternatives
  choice = choice, # column name of choice
  none = None # column name of none alternative
)
```

Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers. We will use the <code>reach()</code> function and use the threshold approach. To specify the bundles we are offering we use the <code>opts</code> argument in our function.

@@

Chrzan, K., & Orme, B. K. (2019). <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.

@@

Miaoulis, G., Parsons, H., & Free, V. (1990). Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
